---
title: "Part 2 Key"
output: html_document
---

Click [HERE](https://docs.google.com/document/d/1KX6_bKA8BOO0NdsUviVi0HCT-q9iTCtTYsS1dGNQJfU/edit?usp=sharing) for the lab prompt. 
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r}
# Attach packages
library(tidyverse)
library(plotly)
library(palmerpenguins)
library(DT)
```


### Part 2: Git version-controlled R Project from scratch

- For this part, you should have created a new repo in GitHub
- Then cloned to create a version-controlled project in R
- Then opened a new .Rmd...and that's where this example starts!
- See the packages you'll need attached above

#### Interactive plot of the penguins

```{r}
penguins_graph <- ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species),
             alpha = 0.4) +
  scale_color_manual(values = c("purple","orange","black")) +
  theme_minimal() +
  labs(x = "flipper length (mm)",
       y = "body mass (g)")

ggplotly(penguins_graph, tooltip = c("species"))


```

#### Interactive table of penguins data with {DT}

```{r}
datatable(penguins)
```

